EDLD 651 Final Project Presentation

### 2020-11-28 presentation.Rmd
update presentation

## Next R hurdle to tackle
- remove outliers and re-run analysis
- run a power analysis
- adapt and develop the study
- run an online study
- replicate with cellular automata and 3D dynamic fractals

>>>>

## Next R hurdle to tackle
- remove outliers and re-run analysis
- run a power analysis
- work with the "random" data
- adapt and develop the study
- run an online study
- replicate with cellular automata and 3D dynamic fractals
